Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-19 code-tests.tex
finished section 4.1, including all of the code comparisons Enzo has been part of.  I decided to move the cosmological code comparisons to this section, rather than putting them down in the test problems in section 4.2 - it just didn't seem to make a ton of sense to do it the other way after I got started.

Over the course of its existence, \enzo\ has been involved in several
comparisons with other astrophysical codes used for self-gravitating
fluid dynamics.

Cosmology: 
Santa Barbara Clusters, \citep{SantaBarbara}.
Enzo-gadget cosmology comparison, \citep{2005ApJS..160....1O}.
Regan et al. Enzo/Gadget Lyman Alpha Forest comparison,
\citep{2007MNRAS.374..196R}.
Heitmann n-body comparison, \citep{2008CS&D....1a5003H}

Hydro:
Agertz hydro comparison, \citep{2007MNRAS.380..963A}.
Tasker test suite, \citep{Tasker2008}.

Turbulence:
Kritsuk supersonic MHD turbulence comparison,
\citep{2011ApJ...737...13K}.  Compares MHD-CT version.

Radiation transport:
Iliev et al. radiation transport comparison, paper II,
\citep{IlievEtAl2009}.  Compares enzo-FLD.

Other:
Turk et al. primordial star formation comparison,
\citep{2011ApJ...726...55T}.  Passy et al. common envelope binary
simulations (SPH-uniform grid comparison), \citep{2012ApJ...744...52P}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Cosmology simulations}
\label{sec.tests.}
\red{(Brian)}
Talk about cosmology code comparisons, where Enzo is good/weak.

>>>>

Over the course of its existence, \enzo\ has been involved in several
comparisons with other astrophysical codes used for self-gravitating
fluid dynamics.  In general, \enzo\ behaves in a manner similar to other
grid-based (and particularly AMR-based) codes, as we will summarize below.

\enzo\ has been involved in several cosmological code comparisons,
including the Santa Barbara Cluster code comparison project
\citep{SantaBarbara}, a large comparison of N-body simulations
\citep{2008CS&D....1a5003H}, as well as several direct comparisons
between \enzo\ and the GADGET SPH code under a variety of
circumstances, including N-body and adiabatic hydrodynamics
\citep{2005ApJS..160....1O,2005MNRAS.364..909V, 2011MNRAS.418..960V}
and simulations of the Lyman-alpha forest \citep{2007MNRAS.374..196R}.
The \enzo\ code typically has a more difficult time resolving
small-scale self-gravitating structures (for an equivalent dark matter
particle count and nominally equivalent force resolution), but does
comparably well as a tree-based code for larger structure, and is
typically superior in terms of resolving fluid features due to its
higher-order (and artificial viscosity-free) hydrodynamics solver.
When examining classical test cases such as the Santa Barbara
project \citep{SantaBarbara}, \enzo\ forms galaxy clusters with very similar density,
temperature, and entropy profiles to other grid-based codes that use
Godunov-type hydro methods, which
systematically differ from particle-based codes using SPH.  Similarly,
in galaxy cluster simulations that look specifically at the properties
of cosmological shocks \citep[e.g.][]{2011MNRAS.418..960V}, \enzo\
produces results that are similar to other high-order grid-based
hydrodynamics codes, and far superior behavior of \enzo\ in
low-density regions when compared to a particle-based code.  In tests
of the Lyman-alpha forest that include radiative cooling and a uniform
metagalactic ultraviolet background, \enzo\ and Gadget provide results
on metrics such as the matter power spectrum that are comparable to
within 5\% \citep{2007MNRAS.374..196R}.

Several comparisons have been made that focus specifically on
hydrodynamics solvers.  In particular, the work of
\citet{2007MNRAS.380..963A} and \citet{Tasker2008} perform
head-to-head comparisons between several grid- and particle-based
codes for a variety of test problems (including shocked gas clouds,
self-gravitating, translating clouds, and Sedov-Taylor explosions),
and show that \enzo\ is comparable or superior in behavior to the
other grid-based hydrodynamics codes involved in the comparison, and
provide useful information on whether an AMR code such as \enzo\
experiences challenges.  More specific comparisons, including one
specifically testing the linear and nonlinear growth of the
Kelvin-Helmholz instability \citep{2012ApJS..201...18M} and one more
broadly examining Galilean invariance in grid-based codes
\citep{2010MNRAS.401.2463R} show that \enzo, and in particular its
implementation of the Piecewise Parabolic Method hydrodynamics solver,
converge to the correct solution as expected, and generally provide
less diffusive solutions than lower-order codes, including those that
use artificial viscosity.  Finally, two code comparison projects have
been undertaken to examine turbulence in hydro codes -- one studied
the behavior of decaying isothermal supersonic turbulence
\citep{2009A&A...508..541K}, and the other looked at supersonic
magnetohydrodynamical turbulence \citep{2011ApJ...737...13K}.  Both
included the \enzo\ code, with the former testing the PPM
hydrodynamics and the latter the constrained transport MHD
implementation.  In both cases, \enzo\ performed similarly to other
grid-based codes that use Godunov-based fluid solvers, and typically
had better effective resolution than particle-based codes using the
same number of particles as the \enzo\ simulation used grid cells.

Three other comparisons between portions of the \enzo\ code and other
simulation tools have been performed in recent years.  The
flux-limited diffusion radiation transport scheme was measured against
several test problems by \citet{IlievEtAl2009}, producing results that
are similar to both expected results and other methods, although there
are some minor differences (although all codes in the study exhibited
differences from the majority of other codes on at least a subset of
the tests).  \citet{2011ApJ...726...55T} shows the result of varied
reaction rate coefficients for the formation of molecular hydrogen via
the 3-body process in both the \enzo\ and Gadget-2 codes.  Similar
trends were visible in both the \enzo\ and Gadget simulations, though
at a nominally equivalent resolution (i.e., with particle and cell gas
masses being comparable) \enzo\ simulations typically displayed a much
higher level of gas structure.  This is unsurprising due to \enzo's
higher-order hydro solver.  Finally, \citet{2012ApJ...744...52P} show
the results of comparing \enzo\ in its non-AMR mode to a
smoothed-particle hydrodynamics code, SNSPH, in the context of
common-envelope binary stellar interactions.  The authors show that
the codes display reasonable convergence properties as a function of
simulation resolution, and also agree quite well with each other --
however, the observed mass-loss rates do not agree particularly well
with observations.

@@
